R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
add urls and table of contents

````
```{r my_chunk_name, my_option="one", my_other_option="two"}
r_code <- do_stuff(to_inputs)
```
````

@@

@@

## TABLE OUTPUT

>>>>

```r
{r my_chunk_name, my_option="one", my_other_option="two"}
```

@@

"Knitting" is the process of taking an R Markdown document and generating its
final output. As a result, options passed to the knit process are "global" (i.e. 
affect the entire document). Most knit options are defined in the YAML header, and
common options include:

- templates, formatting, or other output styles
- parameters
- output document type
-

If your document is very long, a table of contents is very helpful. Unfortunately,
a table of contents is not included in the PhUSE style guide, so we excluded it
from this paper. However, you can easily include a table of contents by adding
a section like the following to your YAML header.

```yaml
output:
  html_document:
    toc: true
```

```yaml
output:
  pdf_document:
    toc: true
```

@@

Often within a research article, report, presentation, or other work, we are standing
on the shoulders of giants. As a result, it is very important that we appropriately reference
their work. External URLs are standard markdown format `[link text](link url)`, and these can
be used to reference internal headers as well. However, for pdf and html document compatibility,
the following is recommended for internal links:

- Label a header with something like `# MY HEADER {#the-header}`
- Reference the header using `\@ref(the-header)`
